\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage{enumitem}

\lstset{basicstyle=\ttfamily, breaklines=true, frame=single}

\begin{document}

\section*{How to Run This Project Locally (Windows)}

Follow these steps in order. You only need to do Steps 1--3 once.

\subsection*{Step 1: Install what you need}

\begin{enumerate}[leftmargin=*]
  \item \textbf{C++ compiler and CMake}
  \begin{itemize}
    \item Install \textbf{MSYS2} or \textbf{MinGW} (for \texttt{g++}), or use \textbf{Visual Studio} with C++ tools.
    \item Install \textbf{CMake} (version 3.16 or newer).
    \item Make sure \texttt{g++} (or \texttt{cl}) and \texttt{cmake} work in your terminal.
  \end{itemize}

  \item \textbf{Ollama} (needed for document embedding and AI chat)
  \begin{itemize}
    \item Download and install from \texttt{https://ollama.com}
    \item Open a new terminal and run:
\begin{lstlisting}
ollama pull nomic-embed-text
ollama pull llama3.2
\end{lstlisting}
    \item Keep Ollama running in the background while you use the RAG features.
  \end{itemize}
\end{enumerate}

\subsection*{Step 2: Open terminal in the project folder}

\begin{lstlisting}
cd "C:\Users\prath\OneDrive\Desktop\C++ Vector Database & RAG Engine"
\end{lstlisting}

\textbf{Important:} Always start the server from this folder. The web UI needs \texttt{index.html} in the current directory.

\subsection*{Step 3: Build the project (first time, or after code changes)}

\textbf{Option A --- CMake (recommended):}
\begin{lstlisting}
cmake -S . -B build
cmake --build build --config Release
\end{lstlisting}

\textbf{Option B --- Quick build script (MinGW only):}
\begin{lstlisting}
build.bat
\end{lstlisting}
This creates \texttt{db.exe} in the project root.

\subsection*{Step 4: Start the server}

\textbf{If you used CMake:}
\begin{lstlisting}
.\build\db.exe
\end{lstlisting}

\textbf{If you used build.bat:}
\begin{lstlisting}
.\db.exe
\end{lstlisting}

You should see output like:
\begin{lstlisting}
=== MY-AI Engine ===
http://localhost:8080
... demo vectors ...
Ollama: ONLINE (or OFFLINE)
\end{lstlisting}

Leave this terminal window open while the server is running.

\subsection*{Step 5: Open the app in your browser}

Go to:
\begin{lstlisting}
http://localhost:8080
\end{lstlisting}

The dashboard loads automatically. You can now search vectors, run benchmarks, insert documents, and ask AI questions.

\subsection*{Quick test (optional)}

In a \textbf{second} terminal (keep the server running in the first):
\begin{lstlisting}
curl http://localhost:8080/status
\end{lstlisting}
You should get a JSON response with project info and Ollama status.

\section*{How to Stop / Close the Project}

\subsection*{Normal way}

\begin{enumerate}[leftmargin=*]
  \item Go to the terminal where the server is running.
  \item Press \textbf{Ctrl + C}.
  \item Wait until the process exits and you get your command prompt back.
  \item Close the browser tab if you want.
\end{enumerate}

That is all. You do not need to stop Ollama unless you want to free memory.

\subsection*{If port 8080 is still in use}

Sometimes the server does not close cleanly. Run:

\begin{lstlisting}
netstat -ano | findstr :8080
\end{lstlisting}

Find the PID (last column), then:

\begin{lstlisting}
taskkill /PID <PID> /F
\end{lstlisting}

Replace \texttt{<PID>} with the actual number (for example, \texttt{12345}).

\section*{Troubleshooting}

\begin{itemize}[leftmargin=*]
  \item \textbf{``index.html not found''} --- You started the server from the wrong folder. Use \texttt{cd} to the project root first.
  \item \textbf{``Failed to bind port 8080''} --- Another program is using port 8080. Stop it with the steps above.
  \item \textbf{Ollama shows OFFLINE} --- Start the Ollama app, then run the \texttt{ollama pull} commands from Step 1.
  \item \textbf{Vector search works but RAG does not} --- RAG needs Ollama online with both models pulled.
\end{itemize}

\end{document}
